On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-30 paper/paper.tex
Clean up a couple of todos and use 'tiny' style for code in appendices

\begin{todo}
  Cite examples where Haskell implementations have been derived specifications.  Conal Elliott's latest two papers (as of May 2020), \cite{Elliott-2018-ad-icfp} and \cite{Elliott2019-convolution-extended}, would be good examples of this. (This is now cited)

@@

\begin{todo}
  Figure out how recursive types fit into this framework. Church encodings can
  handle recursive types and so can our representation. This is also the case
  for Scott encodings, etc, and is the difference between Church and Scott
  encodings.

  Does our way of handling recursive types correspond to how any of
  those encodings handle recursive types?

  Maybe this is relevant: \href{https://www.reddit.com/r/haskell/comments/hvlh6a/generalized_church_encoding_is_the_curryhoward_of/}{\color{blue}{Generalized Church encoding is the Curry-Howard of Knaster-Tarski}}
\end{todo}

@@

\begin{todo}
  \ttt{runIter} has the following alternate implementation. Would this be
  useful to use somewhere?

  \begin{lstlisting}[otherkeywords={}]
  runIter f = getDone . fix (f >=>)

  getDone :: Iter b a -> b
  getDone (Done x) = x
  getDone _ = error "getDone"
  \end{lstlisting}

  where \verb|Iter| is given a standard \verb|Monad| instance (essentially the
  same as the \verb|Either| \verb|Monad| instance). \\

  Maybe this could be useful in some proofs or derivations somewhere (in this
  paper or elsewhere)?

  Note that \verb|error| is never called under any circumstance in this
  implementation of \verb|runIter|.
\end{todo}

@@

\appendix
\section{Additional Code for Standard Haskell Semantics Implementation}
\begin{lstlisting}
absEnv :: forall t. Env -> E t -> t
absEnv env (CaseExp x f) =
  sumMatchAbs f (absEnv env x)

@@

\section{A small EDSL for C code generation used internally by the C backend}
\begin{lstlisting}
type CCode = String
type CName = String

>>>>

\begin{todo}
  % Cite examples where Haskell implementations have been derived specifications.  Conal Elliott's latest two papers (as of May 2020), \cite{Elliott-2018-ad-icfp} and \cite{Elliott2019-convolution-extended}, would be good examples of this. (This is now cited)

@@

% \begin{todo}
%   Figure out how recursive types fit into this framework. Church encodings can
%   handle recursive types and so can our representation. This is also the case
%   for Scott encodings, etc, and is the difference between Church and Scott
%   encodings.

%   Does our way of handling recursive types correspond to how any of
%   those encodings handle recursive types?

%   Maybe this is relevant: \href{https://www.reddit.com/r/haskell/comments/hvlh6a/generalized_church_encoding_is_the_curryhoward_of/}{\color{blue}{Generalized Church encoding is the Curry-Howard of Knaster-Tarski}}
% \end{todo}

@@

% \begin{todo}
%   \ttt{runIter} has the following alternate implementation. Would this be
%   useful to use somewhere?

%   \begin{lstlisting}[otherkeywords={}]
%   runIter f = getDone . fix (f >=>)

%   getDone :: Iter b a -> b
%   getDone (Done x) = x
%   getDone _ = error "getDone"
%   \end{lstlisting}

%   where \verb|Iter| is given a standard \verb|Monad| instance (essentially the
%   same as the \verb|Either| \verb|Monad| instance). \\

%   Maybe this could be useful in some proofs or derivations somewhere (in this
%   paper or elsewhere)?

%   Note that \verb|error| is never called under any circumstance in this
%   implementation of \verb|runIter|.
% \end{todo}

@@

\appendix
\section{Additional Code for Standard Haskell Semantics Implementation}
\begin{lstlisting}[basicstyle=\tiny]
absEnv :: forall t. Env -> E t -> t
absEnv env (CaseExp x f) =
  sumMatchAbs f (absEnv env x)

@@

\vfill\break

\section{A small EDSL for C code generation used internally by the C backend}
\begin{lstlisting}[basicstyle=\tiny]
type CCode = String
type CName = String
